\part{Routine Development}
	From very early on I recognized that a RoboCup Dance \index{routine}routine had to have an interesting routine. It's not all about tech, it's also about the \index{entertainment}entertainment factor.\\
    
    For each level of the competition I have developed a different routine. I always had in mind that I wanted some sort of \index{story}\index{storyline}\hyperref[Story]{storyline} to the performance to provide interest, and draw the audience in. For \index{regionals}Regionals and \index{states}States I didn't create a particular \hyperref[Story]{storyline}, but for \index{nationals}Nationals I've been able to implement a good \hyperref[Story]{storyline}.\\
    
    For Regionals I had a \index{Christmas}Christmas \index{theme}theme, using a \index{Christmas Tree}Christmas tree and presents as props. I animated the \index{regionals}Regionals Routine in around 2 days. I was animating the lights and Christmas tree up until the night before. I feel that the Regionals performance has been the best to date.\\
    
    For \index{States}States I had no particular theme. I didn't really like the States \index{routine}routine - it felt too much like a mashpot of random things that were disjointed and didn't fit together. I feel the reason for this is that I had created the \index{stage}"Stage" \hyperref[Props]{prop} and based the routine around the stage \index{stage}"Stage" \hyperref[Props]{prop}, rather than basing the prop around the routine. It felt rather disjointed, and didn't flow. Rather than the \index{stage}"Stage" \hyperref[Props]{prop} adding to the performance, I felt it subtracted from it. Along with this I had only allowed myself a day to animate the robot, which was not enough to produce a quality performance. You may be wondering why 1-2 days was enough for \index{regionals}Regionals, but not for States - and it's because for Regionals I had the benefit of months to think about what I was going to animate, before \index{animating}animating it. For states I had to come up with what I wanted to animate, and animate it within a day.\\
    
    For Nationals I have a very specific \index{storyline}\hyperref[Story]{storyline}. In essence the \index{nationals}Nationals routine is the essence of what I wanted my routine to always be like. The performance tells a story of a robot and it's creator - a story of \index{rejection}rejection and \index{reconciliation}reconciliation. After the \index{states}states. \\
    
    \input{parts/part_four/chapters/chap_routine_parts}
    
    \input{parts/part_four/chapters/chap_audio}
    
    \input{parts/part_four/chapters/chap_robot_animation}
    
    \input{parts/part_four/chapters/chap_human_performance}
    
    \input{parts/part_four/chapters/chap_props}
    
    \input{parts/part_four/chapters/chap_story}
    
    
    
    
    
    