	\chapter{Props}
    	\label{Props}
        \index{props}
    	Props are to enhance a routine. This is a fatal mistake I made in States.\\
        
        For \index{regionals}Regionals in \index{Rockhampton}Rockhampton, I designed the entire \index{Christmas}Christmas routine, including \index{audio}audio, \index{animating}animating, etc. All the while I was thinking about what props I could use to enhance the routine. This worked really well, and I got a lot of really good props I used to great effect.\\
        
        However, for States I got caught up in trying to create excellent props. The result was that I got a really good \index{stage}"stage" prop - but I put all my time into designing the props, and not enough into routine development. The result was that I created the routine around the props, and not around the music or story.\\
        
        This meant I couldn't \index{animate}animate the routine as well as I wanted, and the story/routine was disjointed and not flowing. I learned my lesson from this, and for \index{nationals}Nationals I have put my efforts into creating the routine.\\
        
        I've found that as I create the routine, I naturally think of funny and engaging props that will enhance the show. When it comes time to adding props, I don't have to put too much effort in, as I already know what I want.\\
        
        For Nationals I had created the \index{story}\hyperref[Story]{storyline} that I wanted and as I was working on animating I realized that having a lab-coat, safety glasses, misc tools scattered around, and some technical panel with dials, buttons, and lights would enhance the routine. Most of these things I have lying around at home, and I can easily put them on a plane.\\
        
        The only thing I'm thinking of working on is the panel with lights and stuff. I put a few hours aside for creating something like that, and programming it.\\
        
        