\chapter{Team}
	\index{Baralaba Robotics}\index{Baralaba}Baralaba Robotics is a team that has been competing in RoboCup for several years. The only "team" member is John Board. John has attended 8 RoboCups at both \index{regional}regional, \index{state}state, and \index{national}national level.\\
	
	\section{John Board}
		\subsection{History}
			Typically in the past Baralaba Robotics has entered the \index{rescue}Rescue divisions with 3 generations of custom built robots.\\
			
			John first heard about RoboCup on TV one evening whilst still living in Brisbane. He saw the soccer robots, and dance robots on TV. He made a commitment to himself at that point that he wanted to competed in that competition one day.\\
			
			After moving to \index{Rockhampton}Rockhampton, John saw an advertisement for RoboCup in 2010. He decided to go along to watch. After seeing the other kids, he thought that he could compete too.\\
			
			The year after in 2011 he entered a modified version of the BOE-Bot from \index{Parallax}Parallax Inc into Rescue.\\
			
			After that John entered several more competitions at State, Regional, and Nationals level. \\
			
			John's most memorable RoboCup was Nationals in \index{Canberra}Canberra, 2012, to which he was sponsored by RCJA QLD to attend. He enjoyed it because although his robot completely bombed out on the day, he was able to talk to a lot of like minded students, and have a lot of memorable experiences in Canberra.\\
			
		\subsection{Media}
        	\index{media}
			John has been no stranger to the media over the years, after being featured in several \index{newspaper}newspaper reports, two \index{TV}TV features, and several other TV appearances.\\
			
			The most recent \index{TV}TV interview can be watched here:\\
			
			\url{https://www.youtube.com/watch?v=OhAaHymBDpM}\\
		
			John's first TV interview meant a lot to him, as he felt the circle had been "completed" - he was first inspired to attend RoboCup from watching kids on TV... he was now able to inspire others through appearing on TV himself.
		
		\subsection{This Year}
			Many people wondered why John switched from \index{Rescue}Rescue to \index{Dance}Dance - as this year is the final year that John Board will be able to compete, he wanted to finish with a bang - and pour all his skills into the \index{dance} division to create an amazing \index{performance}performance.\\
			
			Although typically quite reserved, John has embraced his need to let go a little with the Dance Category - and as such he hopes to provide an interesting \index{counterpointal}counterpointal \index{conversation} between himself and the \index{robotics}robot with dance. \\
			
		\subsection{Next Year}
			People ask me what I would like to do next year - I am \index{goal}goaling to study a \index{Bachelor}Bachelor of \index{Mechatronics}Mechatronics, majoring in \index{Robotics}Robotics and minoring in \index{Areospace}Areospace \index{Avionics}Avionics at \index{QUT}QUT.\\
			
			John has undertake significant Leadership \& Teamwork training with The Boy's Brigade Queensland. This combined with many other events that John has had the opportunity to help organize has provided him with skills he would like to put use organizing events whilst at University.