\chapter{Sharing}
	\label{chap:Sharing}
    \index{sharing}

  I consider information sharing of the utmost importance, including the \index{open source}open source movement. Over the years the openness of the robotics and software community has enabled me to learn what I have. Unusual kindness and time spent on me by \index{community}community members has served as an example on how I can act likewise.\\

  The most notable instance of this took place in 2013. I quickly needed some form of \index{ADC}\index{Analog Digital Converter}ADC for my 2013 \index{Premier Rescue}Premier Robot, \index{Achilles}Achilles. Because I didn't have the time to order an ADC, I asked the \index{Parallax Forum}\index{forums}Parallax Forum community on help to design a cheap ADC-like system using simple electronics. It wouldn't be optimal - but it would be good enough.\\

  One of the (only) Australian members offered that because we lived in the same city, I could drive to his house, and he would give me some \index{MCP3208}MCP3208 \index{SPI}SPI ADCs. After further inquiry I found that he lived only 8 minutes from me!\\

  I promptly drove to his house - and was greeted by his great \index{generosity} in showing me what he does, giving me a tour of his lab, and giving many, many more parts (\index{wires}wires, \index{motors}motors, and other misc electronic \index{components}components for me to play around with).\\

  I believe he also ordered some more ADCs which he sent me in the post - but not only this, he also sent a bunch of other parts, most of which I actually used on the robot!\\

  This, along with the time put into my endeavors on the forums have inspired me to do likewise. I also find it very rewarding sharing what I've learned with others - and seeing how it improves their own robotics. Listed below are a few ways I have been sharing my knowledge:\\
  
  \textbf{Goombungee Exhibit:} The \index{Goombungee}Goombungee \index{exhibit}exhibit, as outlined earlier in this part in the \hyperref[chap:History]{History} chapter, is an example of how I have shared my knowledge by setting up an exhibit and maintaining it for a month. Beyond that I also traveled out to Goombungee and over the weekend I daily held \index{robotics}robotics shows in the local \index{library}library, as well as talking to many locals and tourists about robotics.\\
  
  \textbf{Central Queensland Trip:} After competing in RoboCup Junior Central Queensland, I traveled out to my old hometown, \index{Baralaba}Baralaba. Whilst I was there I gave several \index{talks} talks to primary and highschool \index{students}students, as well as putting on a presentation for the community in the local \index{Ambulance Station}Ambulance Station in both \index{Baralaba}Baralaba and \index{Wowam}Wowan.\\
  
  \textbf{Fiftysix:} \index{FiftySix} I have recently concluded my work \index{writing}writing a \index{curriculum}curriculum for the Fiftysix \index{tablet}Tablet. In this program I teach about the inner workings of a tablet.\\
  
  \textbf{RoboCup Junior Australia:} Where better to share my knowledge about \index{robotics}robotics than at RoboCup! I regularly attend the RoboCup events, and whilst not competing I regularly give the other teams support. An example of this was whilst at \index{RCJCQ}RCJCQ this year I helped fix a \index{mechanical}Mechanical issue on one of the \index{Lego}Lego Dance teams, enabling them to compete. I also regularly assist with \index{programming}programming issues.\\
  
  \textbf{Website, Facebook, Wiki}: As I mentioned in the \hyperref[resources]{Resources} section of the Metadata part, I have recently started pooling my \index{experience}experience onto a \index{Wiki}\hyperref[subsec:Wiki]{Wiki}. I also frequently post what I'm doing with images on Facebook (as also explained in \hyperref[subsec:Facebook]{Facaebook}.\\
    
  \textbf{Contact Details}: I regularly hand out my \index{contact}\hyperref[contact]{contact} details at competitions or other \index{robotics}robotics events, inviting people to contact me if they want to know anything. I have been contact on two or more occasions as a result from this.\\
  
  \textbf{GitHub}: I upload most of the code I write to \index{GitHub}\hyperref[Git]{GitHub}, a free code sharing service, making it available to anyone who would like to look at it. The only times I don't upload to \index{GitHub}\hyperref[Git]{GitHub} is when I have models that potentially breaks \index{copyright}Copyright.\\
  
  \textbf{UQ Robotics Club}: I have had the opportunity to attend the \index{UQ}\index{UQ Robotics Club}UQ Robotics club since 2013. In such time I've been able to help some of the \index{students}students there with projects that they are working on.\\
  
This is just a small swatch of what I do to give back to the \index{community}community that has given the same skills.\\

